Anomalous waves triggered by abrupt depth changes: laboratory experiments and truncated KdV statistical mechanics

### 2020-05-18 paper2_JNLS/Referee Reports/Ref1Response/Ref1.tex
NM

\noindent
\comment{The paper deals with the statistics of the 1D evolution of a surface-gravity-wave field in shallow water, encountering an abrupt depth reduction. The authors perform experimental investigations carried out in a water tank and in parallel they develop a theory based on the statistical mechanics of the Korteveg de Vries equation, used to interpret the experimental results. The two aspects, experimental and theoretical, have been considered before, in References [5] and [25], but here they are put together in an expanded and synergetic way that makes the manuscript clear and interesting. Moreover, although many of the results have been presented before, the analysis of the experimental data of surface slope is new. This is performed in light of the recently derived relationship linking the ratio between displacement skewness and variations of slope variance to the nonlinearity in the system. The agreement of the experimental and theoretical scalings of the ratio is remarkable over a wide range of amplitudes, providing compelling evidence that the theory proposed captures the fundamental, leading-order aspects of the phenomenon.
}
\begin{itemize}
\item We thank the referee for these positive remarks.
\end{itemize}

@@

\begin{itemize}
\item Thank you for these insightful comments which have helped us to improve the discussion of the Gibbs measure throughout the paper. We have added revisions to several key places of the paper, detailed as follows:
\item First, The referee is correct that a sufficient amount of nonlinear interaction is  required for relaxation to the Gibbs measure. We agree that it is most likely the failure of this condition being met that explains the discrepancy between formula (53) and the smallest-amplitude data in Fig. 8(c). We have inserted these points in the updated manuscript. First, see the passage in Section 3.5 (page 11):
\begin{quotation}
We also point out that a sufficient amount of nonlinear mixing is required for relaxation to the above Gibbs measure. In the linearized system, for example, modes propagate without interacting and hence the initial measure induced by the wave generator remains unchanged.
\end{quotation}
Second, see the passage describing Fig. 8(c) in Section 4.4 (page 22)
\begin{quotation}
The apparently less predictable behavior at small amplitudes can be attributed to the fact that, in order for the system to relax to the Gibbs measure, modes must interact through nonlinearity. For the smallest amplitude experiments, the amount of nonlinearity is apparently too small for  modes to mix sufficiently.
\end{quotation}
%
\item We thank the referee for drawing our attention to the vibrant field of integrable turbulence. We have now included a discussion to compare and contrast our statistical theory with those stemming from integrable turbulence (and included a few key references). In particular, please see the new passage at the end of section 3.4
\begin{quotation}
We comment on some important differences between the KdV and TKdV dynamical systems. Besides momentum, energy, and Hamiltonian, KdV possesses in infinite sequence of additional invariants. Trajectories of KdV are therefore constrained by an infinite number of conserved quantities, associated with the fact that it is a completely integrable system whose long-time dynamics are dominated by coherent structures known as solitons. The analogues of these additional invari- ants, however, are not generally conserved in the truncated system; the only known invariants of TKdV are the three mentioned already: momentum, energy, and Hamiltonian. Dynamics of TKdV, rather than being dominated by coherent structures, become chaotic in long time and have been numerically observed to satisfy weak ergodicity (though a rigorous mathematical proof awaits) [2]. In this way, the theory developed herein differs from, and could likely complement, recent advances in the field of integrable turbulence [54, 40, 10, 41], where integrability is exploited to uncover certain statistical features. We remind the reader that KdV is asymptotically valid only for large spatial scales and hence truncating the small scales does not alter the order of approximation made. In this sense, KdV and TKdV should be regarded as on equal footing as far as physical realism, provided that sufficiently many modes are considered. Where differences exist in long-time dynamics, it is unclear a priori which model, if either, more closely resembles reality, which underscores the importance of controlled laboratory experiments.
\end{quotation}
\end{itemize}
%\item The referee is correct that equilibrium statistical mechanics and the canonical ensemble is used here, not because it is rigorously justified, but as an effective theory that explains the data.

@@

\begin{itemize}
\item Thank you for bringing this very relevant reference to our attention. We included this reference and, in addition, have found another reference, Onorato \& Suret 2016, which has analysis specific to KdV. We have now included a discussion of these works, including similarities and differences with our analysis. In particular, note that both of these references considered only uniform depth, whereas, since our work considers variable depth, it must account for the transfer of information from one depth to another. This link is provided by the statistical matching condition, which is the key to derive equation (53). See the passage at the end of Section 4.4:

@@

It is conceivable that bound modes could contribute somewhat to the downstream skewness, but we point out that we went to great lengths in the experiments to mitigate the effects of bound modes. In particular, we installed a wave dampener at the far end of the tank, which, after making efforts to optimize our design, we found successful eliminates 90\% of reflections from the far end. See again Bolles et al.~2019 for even more details. It is possible that reflections could be controlled to an even greater degree through electronic feedback systems, such as those present in the Hydrodynamics laboratory facilities at Imperial College of London, but we leave that for future work. It is also conceivable that one could create a data processing method to attempt to filter out the bound modes, but seeing as our theory successful captures the observed skewness transitions, we prefer to avoid the possible ambiguities and uncertainties introduced by an extra layer of data manipulation. 
This is not to say that there is anything wrong with filtering data, it is simply a philosophical position: we aim to develop a parsimonious theory that explains and predicts the experimental data in its raw state, or as close to that state as possible.
\end{itemize}

@@

>>>>

\noindent
\comment{The paper deals with the statistics of the 1D evolution of a surface-gravity-wave field in shallow water, encountering an abrupt depth reduction. The authors perform experimental investigations carried out in a water tank and in parallel they develop a theory based on the statistical mechanics of the Korteveg de Vries equation, used to interpret the experimental results. The two aspects, experimental and theoretical, have been considered before, in References [5] and [25], but here they are put together in an expanded and synergetic way that makes the manuscript clear and interesting. Moreover, although many of the results have been presented before, the analysis of the experimental data of surface slope is new. This is performed in light of the recently derived relationship linking the ratio between displacement skewness and variations of slope variance to the nonlinearity in the system. The agreement of the experimental and theoretical scalings of the ratio is remarkable over a wide range of amplitudes, providing compelling evidence that the theory proposed captures the fundamental, leading-order aspects of the phenomenon.
}

\noindent
\\We thank the referee for these positive remarks. \\ \\

@@

\begin{itemize}
\item Thank you for these insightful comments which have helped us to improve the discussion of the Gibbs measure throughout the paper. We have added revisions to several key places of the paper, detailed as follows:
\item First, The referee is correct that a sufficient amount of nonlinear interaction is  required for relaxation to the Gibbs measure. We agree that it is most likely the failure of this condition being met that explains the discrepancy between formula (53) and the smallest-amplitude data in Fig. 8(c). We have inserted these points in the updated manuscript. First, see the passage in Section 3.5 (page 11):
\begin{quotation}
We also point out that a sufficient amount of nonlinear mixing is required for relaxation to the above Gibbs measure. In the linearized system, for example, modes propagate without interacting and hence the initial measure induced by the wave generator remains unchanged.
\end{quotation}
Second, see the passage describing Fig. 8(c) in Section 4.4 (page 22)
\begin{quotation}
The apparently less predictable behavior at small amplitudes can be attributed to the fact that, in order for the system to relax to the Gibbs measure, modes must interact through nonlinearity. For the smallest amplitude experiments, the amount of nonlinearity is apparently too small for  modes to mix sufficiently.
\end{quotation}
%
\item We thank the referee for drawing our attention to the vibrant field of integrable turbulence. We have now included a discussion to compare and contrast our statistical theory with those stemming from integrable turbulence (and included a few key references). In particular, please see the new passage at the end of section 3.4
\begin{quotation}
We comment on some important differences between the KdV and TKdV dynamical systems. Besides momentum, energy, and Hamiltonian, KdV possesses in infinite sequence of additional invariants [26, 52]. Trajectories of KdV are therefore constrained by an infinite number of conserved quantities, associated with the fact that it is a completely integrable system whose long-time dynamics are dominated by coherent structures known as solitons. The analogues of the additional invariants, however, are not generally conserved in the truncated system; the only known invariants of TKdV are the three mentioned already: momentum, energy, and Hamiltonian. Dynamics of TKdV, rather than being dominated by coherent structures, become chaotic in long time and have been numerically observed to satisfy weak ergodicity (though a rigorous proof awaits) [2]. In this way, the theory developed herein differs from, and could likely complement, recent advances in the field of integrable turbulence [54, 40, 10, 41], where integrability is exploited to uncover certain statistical features of the system at hand. We remind the reader that KdV is asymptotically valid only for large spatial scales, and hence truncating the small scales does not alter the order of approximation made. In this sense, KdV and TKdV are on equal footing as far as physical realism – a more accurate framework would require either model closure to capture the small scale physics or else direct numerical simulation of the Euler equations. Where differences exist between KdV and TKdV, therefore, it is unclear a priori which model, if either, more closely resembles reality. This situation, of course, underscores the importance of controlled laboratory experiments.
\end{quotation}
\end{itemize}
%\item The referee is correct that equilibrium statistical mechanics and the canonical ensemble is used here, not because it is rigorously justified, but as an effective theory that explains the data.

@@

\begin{itemize}
\item Thank you for bringing this reference to our attention. We have included this reference and, in addition, have found another reference, Onorato \& Suret 2016, which contains similar analysis that is specific to KdV. In the revised manuscript, we have added a discussion of these works, including similarities and differences with our analysis. In particular, note that both of these references considered only uniform depth, whereas, since our work considers variable depth, it must account for the transfer of information from one depth to another. This link is provided by the statistical matching condition, which is the key to derive equation (53). See the passage at the end of Section 4.4:

@@

It is conceivable that bound modes could contribute somewhat to the downstream skewness, but we would like to point out that careful measures were taken to mitigate the effects of bound modes in the experiments. In particular, we installed a wave dampener at the far end of the tank, which, after some considerable design optimization, was found to successfully eliminate 90\% of reflections from the far end. See Bolles et al.~2019 for even more details. It is possible that reflections could be controlled to an even greater degree through electronic feedback systems, such as those present in the Hydrodynamics Laboratory facilities at Imperial College of London, but we leave that task for future work. It is also conceivable that one could create a data processing method to filter out the bound modes, but, seeing as our theory successful captures the observed skewness transitions, we would prefer to avoid the possible ambiguities and uncertainties introduced by an extra layer of data manipulation. 
Philosophically, we strive for a parsimonious model that explains and predicts the experimental data in its raw state, or as close to that state as possible, and we believe that goal has been met.
\end{itemize}
%This is not to say that there is anything wrong with filtering data, it is simply a philosophical position: we aim to develop a parsimonious theory that explains and predicts the experimental data in its raw state, or as close to that state as possible.

@@

\noindent
\\We thank the referee for these kind remarks.
